*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-22 Code/Manuscript_O2.Rmd
Knit changes

The growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
(Figure \@ref(fig:MED4PAR)), under 250 µM O~2~. No growth was
observed under any imposed conditions under a 4 h photoperiod. MED4 was
able to grow under the lowest PAR treatment of 30 µmol photons m^-2^
s^-1^ but only when the blue light photoperiod was longer than 4 h; the
white LED light photoperiod was longer than 8 h; or when the red light
photoperiod was longer than 16 h. Growth rate increased
with increasing photoperiods for all spectral wavebands when exposed to
PAR of 90 and 180 µmol photons m^-2^ s^-1^. MED4 grew fastest for each
spectral waveband under 16 h photoperiods. The maximum growth rate
(µ~max~) was
`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
d^-1^ achieved under 180 uE blue
light and 16 h photoperiod.

@@

Similar to the growth trends under 250 µM O~2~, MED4
maintained at 25 µM O~2~ showed the fastest growth rates when the
photoperiod was 16 h for each spectral waveband, across PAR levels
(Figure \@ref(fig:MED4PAR)). The 25 µM O~2~ growth experiments showed
generally similar growth rates as the 250 µM O~2~ growth experiments,
with the interesting exception that growth rates increased by 40% under
25 µM O~2~ at PAR of 30 µmol photons m^-2^ s^-1^ and 16 h photoperiod,
and even showed growth under 12 h red light photoperiod, in contrast to
the 250 µM O~2~ growth experiments. White LED light treatments grew
slower, if at all, under 25 µM O~2~, only growing under higher PAR of 90
and 180 µmol photons m^-2^ s^-1^ and longer photoperiods of 12 and 16 h.
As under 250 µM O~2~, the fastest growth rate observed for each spectral
waveband at each imposed PAR were greatest under the 16 h photoperiod.
The µ~max~ was
`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
d^-1^  achieved under 180 µmol photons
m^-2^ s^-1^ blue light and 16 h photoperiod. The 4 h photoperiod
experiments under white LED light were not performed because no growth
was achieved when grown under an 8 h photoperiod.

>>>>

The growth rates of *P. marinus* MED4, Clade HLI, increased with higher imposed PAR and longer photoperiods
(Figure \@ref(fig:MED4PAR)), under 250 µM O~2~. No growth was
observed under any imposed conditions under a 4 h photoperiod. MED4 was
able to grow under the lowest PAR treatment of 30 µmol photons m^-2^
s^-1^ but only when the blue light photoperiod was longer than 4 h and the white LED and red light photoperiod was longer than 8 h. Growth rate increased
with increasing photoperiods for all spectral wavebands when exposed to
PAR of 90 and 180 µmol photons m^-2^ s^-1^. MED4 grew fastest for each
spectral waveband under 16 h photoperiods. The maximum growth rate
(µ~max~) was
`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "250", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
d^-1^ achieved under 180 uE blue
light and 16 h photoperiod.

@@

Similar to the growth trends under 250 µM O~2~, MED4
maintained at 25 µM O~2~ showed the fastest growth rates when the
photoperiod was 16 h for each spectral waveband, across PAR levels
(Figure \@ref(fig:MED4PAR)). The 25 µM O~2~ growth experiments showed
generally similar growth rates as the 250 µM O~2~ growth experiments,
with the interesting exception that growth rates increased by 40 % under
25 µM O~2~ at PAR of 30 µmol photons m^-2^ s^-1^ and 16 h blue photoperiod and increased by 55 % under 16 h red photoperiod, in contrast to
the 250 µM O~2~ growth experiments. White LED light treatments grew
slower, if at all, under 25 µM O~2~, only growing under higher PAR of 90 µmol photons m^-2^ s^-1^ and 16 h photoperiod and 180 µmol photons m^-2^ s^-1^ and 12 and 16 h photoperiods.
As under 250 µM O~2~, the fastest growth rate observed for each spectral
waveband at each imposed PAR were greatest under the 16 h photoperiod.
The µ~max~ was
`r PURPARFits %>% filter(Strain == "MED4", WL == "450", O2_uM == "25", Photoperiod == 16) %>% select(ReplicateMean_deltaOD_Lmu_corr_day) %>% max() %>% round(digits = 2)`
d^-1^  achieved under 180 µmol photons
m^-2^ s^-1^ blue light and 16 h photoperiod. The 4 h photoperiod
experiments under white LED light were not performed because no growth
was achieved when grown under an 8 h photoperiod.
